---
title: "SBM Report Group 4"
format: html
editor: visual
author: "Bram, Diego, Roland, Thomas, Borná"
bibliography: references.bib
---

# Report SBM Group 4

## Introduction

Introduce the topic, explain why it is interesting (the research gap and the practical relevance), and formulate the research question.

## Theory and Hypotheses

Explain the state of art in the relevant literature, building towards what is it exactly that you would like to research, consistent with your research question and research gap. If your research design allows for it, develop at most 3 hypotheses based on the theoretical framework you covered: what is it that you expect to see in the data, and why? (Include Behavioral Theory of the Firm).

### Assumptions

We assume that an entrepreneur does not have any prior experience. We assume that the data is sufficient. For a proxy of successrate, we use the funding as a measure. We assume that the funding is a good proxy for success, because if the funding is not met, the project will not be realized. We assume that the data is not biased, because the data is collected by a third party. We assume that the data is not biased, because the data is collected by a third party. We assume that innovation-related words can also be taken as meaning innovation. By expanding the bucket of words referring to innovation we assure that the majority of the words related to innovation are covered.

We do not assume that employees influence business results, as we are taking a look at Kickstarter projects. And start-up culture is not the same as corporate culture. We do not assume that the number of employees is a good proxy for experience, because the number of employees does not say anything about the experience of the employees [@martin2010].

### Research Question 1

How does experience impact the success rate?

Hypothesis 1: Experience will have a positive impact on whether the idea is successful.

### Research Question 2

How do business ideas change after experience?

Hypothesis 2: subsequent ideas are more innovative than the first idea.

## Methods and Data

Describe the data set that you used, the way you translated the raw data into variables, and the methods you used to analyze the data (e.g., cluster analysis, regression analysis, panel data analysis, time series). Remember that most methods have a number of assumptions that you have to check prior to doing the analyses. Certain assumption violations can be fixed by transforming the focal variables, e.g., the dependent variable, in case of other violations you may need to choose a different method.

```{r}
getwd()
set.seed(231)
#setwd("C:/Users/Borna/Documents/Study/Masters/Master A/Strategy and Business Models/SBM_assignment/report")data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAACgAAAAaCAYAAADFTB7LAAAAa0lEQVR42u3OywnAIBBAwcXSUoCW5D11xDoNCBGNv0MOecJOBSOi1OZMsJ4dvFxEJ1OQnMxBarIKEpNNkJbsBknJYZCSnAYJyVVQziNig7/nZkFEbhTE5HpBVO4dxOXKIDL3BLG5BJ1T6rsbMfep2CaMN00AAAAASUVORK5CYII=
#getwd()
```

### Data Importing and cleaning, hypothesis 1

In order to test the first hypothesis it is necessary to first clean the data. The first step is to select the data that has a deadline is before week 32 in 2019 in unix time and make sure that the variables that will be used in the regression are of the correct class. Next, a percentage is derived from the pledge goal of the project and how much was actually pledged, this will be used as a measure of success. For this reason the projects with a pledge goal of 0 were removed, this avoids division by zero. It was also chosen that values that exceeded 100% would be set to this value, as these might be detected as outliers and could cause issues. After this, we check the distribution of the data and remove cases in which we don't have enough data for the number of projects backed and the number of projects created, which are proxies for learning in this study. We consider that having less than 50 data points is when the data point is removed, this is because 50 data points are the minimum for a normal distribution to be present (find citation). Finally, the null values are removed. The below shows the distribution of the learning proxies and the proxy for success.

```{r}

#inspect the data
info32

#create new data with only a few columns of info32 dataset
dataHyp1Sub <- info32[,c('Goal_USD','Pledge_USD','Launched_at','Deadline', 'Creator_nb_projects', 'Creator_nb_backed')]
#dataHyp1Sub

#make a subdataset where deadline is before week 32 in 2019 in unix time
dataHyp1 <- dataHyp1Sub[dataHyp1Sub$Deadline < 1565474400,]
#dataHyp1

#You drop only 1850 records out of 75000

#count the number of rows in dataHyp1sub and dataHyp1
nrow(dataHyp1Sub)
nrow(dataHyp1)


#columns to integer
dataHyp1$Pledge_USD <- as.integer(dataHyp1$Pledge_USD)
dataHyp1$Goal_USD <- as.integer(dataHyp1$Goal_USD)

#drop the rows where Goal_USD is 0 -> then you might get inf percentage
dataHyp1 <- dataHyp1[dataHyp1$Goal_USD != 0,]
#dataHyp1

#Create a new column with percentage of goal reached
dataHyp1$Goal_percentage <- dataHyp1$Pledge_USD/dataHyp1$Goal_USD
dataHyp1$Goal_percentage <- round(dataHyp1$Goal_percentage, digits = 3)
dataHyp1$Goal_percentage[dataHyp1$Goal_percentage>100] = 100
print(dataHyp1$Goal_percentage)
#dataHyp1

#Get from Creator_nb_backed only the number with a regex
dataHyp1$Creator_nb_backed <- gsub("[^0-9]", "", dataHyp1$Creator_nb_backed) #Seeing if this works better as a string rather than
#dataHyp1

#drop redundant columns
dataHyp1 <- dataHyp1[,c('Creator_nb_projects', 'Creator_nb_backed', 'Goal_percentage')]


#Drop the rows where nan values occur
dataHyp1 <- dataHyp1[complete.cases(dataHyp1),]


#dataHyp1#Columns as integers
#dataHyp1$Creator_nb_backed <- as.integer(dataHyp1$Creator_nb_backed)


#to find an appropriate cutoff point:
table(dataHyp1$Creator_nb_projects)
table(dataHyp1$Creator_nb_backed)

# we will only use values with at least 50 records, because for normal distribution you need a minimum of 50 values
# So then you have an substantial amount of values


#iterate over the values of the following table: table(dataHyp1$Creator_nb_projects)
quan_table1 = table(dataHyp1$Creator_nb_projects)
quan_table2 = table(dataHyp1$Creator_nb_backed)

#in quan_table, drop the records where the value is < 50
quan_table1 <- quan_table1[quan_table1 >= 50]
quan_table2 <- quan_table2[quan_table2 >= 50]

#clean the data such that only records with over 50 occurences are in there
dataHyp1_2 <- dataHyp1[dataHyp1$Creator_nb_projects %in% names(quan_table1),]
dataHyp1_2 <- dataHyp1[dataHyp1$Creator_nb_backed %in% names(quan_table2),]

#make a table of the values of Creator_nb_projects
table(dataHyp1_2$Creator_nb_projects)

#drop nan and inf values in dataHyp1_2
dataHyp1_2 <- dataHyp1_2[complete.cases(dataHyp1_2),]


#dataHyp1_2


####I think this below is the old stuff, the newer stuff contained percentages

#make a new column with boolean if goal_USD >= Pledge_USD
#dataHyp1$Goal_met <- dataHyp1$Goal_USD <= dataHyp1$Pledge_USD
#dataHyp1

#Get from Creator_nb_backed only the number with a regex
#dataHyp1$Creator_nb_backed <- as.integer(gsub("[^0-9]", "", dataHyp1$Creator_nb_backed))

#drop na values in dataHyp1
#dataHyp1 <- dataHyp1[complete.cases(dataHyp1),]
#dataHyp1 <- dataHyp1[,c('Creator_nb_projects', 'Creator_nb_backed', 'Goal_met')]
#dataHyp1


#change Goal_met to binary
#dataHyp1$Goal_met <- as.integer(dataHyp1$Goal_met)
#dataHyp1


#Columns as integers
#dataHyp1$Creator_nb_backed <- as.integer#(dataHyp1$Creator_nb_backed)


#to find an appropriate cutoff point:
#table(dataHyp1$Creator_nb_projects)

# we will only use values with at least 50 records, because for normal distribution you need a minimum of 50 values
# So then you have an substantial amount of values


#iterate over the values of the following table: table(dataHyp1$Creator_nb_projects)
#quan_table = table(dataHyp1$Creator_nb_projects)

#in quan_table, drop the records where the value is < 50
#quan_table <- quan_table[quan_table >= 50]

#clean the data such that only records with over 50 occurences are in there
#dataHyp1_2 <- dataHyp1[dataHyp1$Creator_nb_projects %in% names(quan_table),]

#make a table of the values of Creator_nb_projects
#table(dataHyp1_2$Creator_nb_projects)



```

Next we check the distribution of the success proxy. We notice that it is not normal, so a couple of transformations are tried. First Log(x+1) is tried, given that 0% is still viable, this shift is necessary to avoid undefined values. Next sqrt(Log(x+1)) is applied, but even though it is better, with the QQ-plots below we notice that it is still not normally distributed. The first QQ-plot corresponds to Log(x+1) and the second is for sqrt(Log(x+1)). Therefore a Linear Regression model cannot be used.

```{r}
x<-dataHyp1_2$Goal_percentage
##check the distribution of the outcome variable
hist(x)
table(x)
#looks exponential, so we try log transform
y<-log(dataHyp1_2$Goal_percentage+1)
qqnorm(y)
qqline(y)
#still skewed, so we try to include sqrt transform
y<-sqrt(log(dataHyp1_2$Goal_percentage+1))
qqnorm(y)
qqline(y)


```

### Regression and Anova test, hypothesis 1

Given that the data is not normally distributed, and the tested transformations are not satisfactory a linear regression is not appropriate. By looking at the previous histogram, we can asses that the data seems to be from an exponential distribution with an inflated 0 value. Therefore, Poisson regression Gamma regression, and zero inflated regression are tried. For poisson regression, we round the goal percentage to the nearest integer, given that the model works for discrete outcome variables. It is also important to note that the zero inflated value model did not converge, regardless of the preprocessing steps taken for this regression. The first step was hot-encoding the proxies for learning because the model doesn't take factors as inputs, then the percentages for the success were rounded to integers because the model only outputs integers. The possible reasons as to why this error still occured will be presented in the discussion section.

```{r}

##non integer

##try Gamma distribution

dataHyp1_2$nonzero_percentage <- dataHyp1_2$Goal_percentage + 1e-6
modelGamma  <- glm(nonzero_percentage ~ Creator_nb_projects + Creator_nb_backed, data = dataHyp1_2,family = Gamma(link = 'identity'))

dataHyp1_2$Goal_percentage_int <- as.integer(round(dataHyp1_2$Goal_percentage,0))
##poisson distribution int

modelPoissonInt <- glm(Goal_percentage_int ~ Creator_nb_projects + Creator_nb_backed, data = dataHyp1_2,family = poisson(link = 'log'))


# trying zero inflation model
##can't use factors, need to one hot encode



hot_encode <- model.matrix(~  Creator_nb_projects + Creator_nb_backed  - 1, data = dataHyp1_2)

hot_encode<-as.data.frame(hot_encode)

##can't use non integer values for the dependent variable

inflDS <- cbind(dataHyp1_2$Goal_percentage, hot_encode)

#don't run this if the second zeroinfl will be runned (it will cause issues with removing values to try to avoid skeweness)
inflDS$percent_int<- as.integer(round(inflDS$`dataHyp1_2$Goal_percentage`,0))

null_values_per_column <- sapply(inflDS, function(x) any(is.na(x)))

# Print the result

##doesn't converge
modelZeroINFL_1 <- pscl::zeroinfl(percent_int ~ . - `dataHyp1_2$Goal_percentage` | . - `dataHyp1_2$Goal_percentage`, dist = "geometric", data = inflDS, control = pscl::zeroinfl.control(maxit = 100000))

##try to remove skeweness by ignoring certain values (between 0 an 1, to avoid having too much data)

inflDS<- inflDS[!(inflDS$`dataHyp1_2$Goal_percentage` > 0 & inflDS$`dataHyp1_2$Goal_percentage` < 1), ]
inflDS$percent_int<- as.integer(round(inflDS$`dataHyp1_2$Goal_percentage`,0))


##doesn't converge either
modelZeroINFL_2 <- pscl::zeroinfl(percent_int ~ . - `dataHyp1_2$Goal_percentage` | . - `dataHyp1_2$Goal_percentage`, dist = "geometric", data = inflDS, control = pscl::zeroinfl.control(maxit = 100000))
summary(modelZeroINFL)





###This is also old for the same reason as the previous


#make a reg model to predict goal_met with Creator_nb_projects and Creator_nb_backed
#modelHyp1 <- lm(Goal_met ~ Creator_nb_projects + Creator_nb_backed, data = dataHyp1_2)

#make a logreg model to predict goal_met with Creator_nb_projects and Creator_nb_backed
#modelHyp1Log <- glm(Goal_met ~ Creator_nb_projects + Creator_nb_backed, data = dataHyp1_2, family = "binomial")
#summary(modelHyp1Log)



#Perform anova test on dataHyp1

#Anova_normal <- anova(modelHyp1)
#Anova_log <- anova(modelHyp1Log)

#stargazer::stargazer(list(Anova_normal, Anova_log), type = 'text')

#table output both Anova_normal and Anova_log inline using stargazer
```

Given that the models are part of the Generalized Linear Model class, an Analysis of Deviance can be used. This tells us whether including a certain variable is significant for a better prediction of the dependent variable, therefore indicating whether a variable is important when predicting the success of a Kickstarter project.

### Some more cleaning and barplot creation

Roland: I don't know what this is to be honest.

```{r}
# #return the values of the loop in a vector
# vec_val <- c()
# vec_ind <- c()
# vec_amount <- c()
# 
# for (i in 1:as.integer(max(dataHyp1$Creator_nb_projects))){
#   vec_val[i] <- sum(dataHyp1$Goal_met[dataHyp1$Creator_nb_projects == i])/length(dataHyp1$Goal_met[dataHyp1$Creator_nb_projects == i])
#   vec_ind[i] <- i
#   vec_amount[i] <- length(dataHyp1$Goal_met[dataHyp1$Creator_nb_projects == i])
# }
# 
# #create a table of vec_val and vec_ind as two columns with headers: index and percentage
# tableHyp1 <- data.frame(vec_ind, vec_val, vec_amount)
# tableHyp1



```

```{r}
# #make a barplot of the column vec_amount
# barplot(tableHyp1$vec_amount, names.arg = tableHyp1$vec_ind, xlab = "Number of projects", ylab = "Number of projects of the creator", main = "Number of projects of the creator by number of projects of the creator")

```

```{r}


# #drop columns where nan exists
# tableHyp1 <- tableHyp1[complete.cases(tableHyp1),]
# # tableHyp1
# 
# 
# #make a barchart of tableHyp1
# barplot(tableHyp1$vec_val, names.arg = tableHyp1$vec_ind, xlab = "Number of projects", ylab = "Percentage of projects that met their goal", main = "Percentage of projects that met their goal by number of projects of the creator")


```

```{r}
# #make a barchart of the number of projects per number of projects
# barplot(tableHyp1$vec_amount, names.arg = tableHyp1$vec_ind, xlab = "Number of projects", ylab = "Number of projects of the creator", main = "Number of projects of the creator by number of projects of the creator")


```

```{r}

# # Convert the data to numeric if needed
# dataHyp1$Creator_nb_projects <- as.numeric(dataHyp1$Creator_nb_projects)
# 
# # Check if 'tableHyp1$vec_ind' is numeric or convert it
# tableHyp1$vec_ind <- as.numeric(tableHyp1$vec_ind)
# 
# # Now, create the barplot
# barplot(dataHyp1$Creator_nb_projects, names.arg = tableHyp1$vec_ind, xlab = "x", ylab = "y", main = "title")
# 
# #this code raises an error. 


```

## Results

### Hypothesis 1 results

Given that the zero inflated model doesn't produce results, we proceed by studying the Poisson and Gamma models. First we look at the results for the Poisson Model.

```{r}
##Poisson summary
summary(modelPoissonInt)


# dataHyp1
# dataHyp1$Creator_nb_projects
# tableHyp1$vec_ind

```

From the results we see that most of the coefficients for both the number of backed projects and the number of projects created are significant. This suggests that the effects of the proxies we selected for learning are significant. In regards to the sign of the coefficients, we notice that none of the negative values are significant, with the exception of the intercept. Since the significant coefficients are positive, though small, we conclude that learning has a positive effect on success, which is in line with (find citation). In this case we don't notice an increasing pattern in of the coefficients, wherein more experience would have significantly higher values, as sometimes the coefficients decrease again.

```{r}
#Anova Poisson
anova(modelPoissonInt)
```

In the analysis of deviance table we notice that the inclusion of the number of projects backed reduces the deviance by a large margin, this justifies including these variables in the model, as it results in a better model.

```{r}
#Sumary for Gamma model
summary(modelGamma)
```

For this model, we notice that the coefficients are not mostly significant in the case of the number of projects created; contrastingly, the number of projects backed does have mostly significant values. It is also important to note that this Gamma distribution model has a lower AIC than the Poisson distribution model. We also notice that if the values are placed in increasing order of the amounts projects back and of the number of projects created there is an increase in the coefficients. This suggests that the more experience one has, the better they tend to perform. We also notice that the values that don't follow this tendency don't have significant p-values.

```{r}
#Anova Gamma
anova(modelGamma)
```

In this second analysis of deviance table, a similar effect is noticed to the previous, including the number of projects backed improves the model by reducing the deviance, which suggests that it's a good variable for the model. Therefore we can say that the success is not just explained by the experience one gains by doing more projects, but also observing the projects of others.

Present the results of your analyses including descriptive statistics, regression tables, as well as any possible figures or visualizations that you made, e.g., those of the interaction effects.

## Discussion

What did we learn from what you found in your results, how do those findings relate to the ongoing debate in literature, and what can practitioners learn from that?

## Conclusion (?)

The description did not say a conclusion was needed, but I think it is a good idea to have one.

## References

the bib.tex file can go here. I have not yet added any references, but as we write they will be added.
