---
title: "SBM Report Group 4"
format: html
editor: visual
author: "Bram, Diego, Roland, Thomas, Borná"
---

# Report SBM Group 4

## Introduction

Introduce the topic, explain why it is interesting (the research gap and the practical relevance), and formulate the research question.

## Theory and Hypotheses

Explain the state of art in the relevant literature, building towards what is it exactly that you would like to research, consistent with your research question and research gap. If your research design allows for it, develop at most 3 hypotheses based on the theoretical framework you covered: what is it that you expect to see in the data, and why?

### Research Question 1

How does experience impact the success rate?

Hypothesis 1: Experience will have a positive impact on whether the idea is successful.

### Research Question 2

How do business ideas change after experience?
Hypothesis 2: 

## Methods and Data

Describe the data set that you used, the way you translated the raw data into variables, and the methods you used to analyze the data (e.g., cluster analysis, regression analysis, panel data analysis, time series). Remember that most methods have a number of assumptions that you have to check prior to doing the analyses. Certain assumption violations can be fixed by transforming the focal variables, e.g., the dependent variable, in case of other violations you may need to choose a different method.

### Data Importing and cleaning, hypothesis 1

```{r}
#inspect the data
info32

#create new data with only a few columns of info32 dataset
dataHyp1Sub <- info32[,c('Goal_USD','Pledge_USD','Launched_at','Deadline', 'Creator_nb_projects', 'Creator_nb_backed')]
#dataHyp1Sub

#make a subdataset where deadline is before week 32 in 2019 in unix time
dataHyp1 <- dataHyp1Sub[dataHyp1Sub$Deadline < 1565474400,]
#dataHyp1

#You drop only 1850 records out of 75000

#count the number of rows in dataHyp1sub and dataHyp1
nrow(dataHyp1Sub)
nrow(dataHyp1)


#make a new column with boolean if goal_USD >= Pledge_USD
dataHyp1$Goal_met <- dataHyp1$Goal_USD <= dataHyp1$Pledge_USD
#dataHyp1

#Get from Creator_nb_backed only the number with a regex
dataHyp1$Creator_nb_backed <- as.integer(gsub("[^0-9]", "", dataHyp1$Creator_nb_backed))

#drop na values in dataHyp1
dataHyp1 <- dataHyp1[complete.cases(dataHyp1),]
dataHyp1 <- dataHyp1[,c('Creator_nb_projects', 'Creator_nb_backed', 'Goal_met')]
#dataHyp1


#change Goal_met to binary
dataHyp1$Goal_met <- as.integer(dataHyp1$Goal_met)
#dataHyp1


#Columns as integers
dataHyp1$Creator_nb_backed <- as.integer(dataHyp1$Creator_nb_backed)


#to find an appropriate cutoff point:
table(dataHyp1$Creator_nb_projects)

# we will only use values with at least 50 records, because for normal distribution you need a minimum of 50 values
# So then you have an substantial amount of values


#iterate over the values of the following table: table(dataHyp1$Creator_nb_projects)
quan_table = table(dataHyp1$Creator_nb_projects)

#in quan_table, drop the records where the value is < 50
quan_table <- quan_table[quan_table >= 50]

#clean the data such that only records with over 50 occurences are in there
dataHyp1_2 <- dataHyp1[dataHyp1$Creator_nb_projects %in% names(quan_table),]

#make a table of the values of Creator_nb_projects
table(dataHyp1_2$Creator_nb_projects)



```

### Anova test, hypothesis 1

```{r}
#make a logreg model to predict goal_met with Creator_nb_projects and Creator_nb_backed
modelHyp1Log <- glm(Goal_met ~ Creator_nb_projects + Creator_nb_backed, data = dataHyp1_2, family = "binomial")
summary(modelHyp1Log)

#Perform anova test on dataHyp1
anova(modelHyp1)

```

### Some more cleaning and barplot creation

```{r}
#return the values of the loop in a vector
vec_val <- c()
vec_ind <- c()
vec_amount <- c()

for (i in 1:as.integer(max(dataHyp1$Creator_nb_projects))){
  vec_val[i] <- sum(dataHyp1$Goal_met[dataHyp1$Creator_nb_projects == i])/length(dataHyp1$Goal_met[dataHyp1$Creator_nb_projects == i])
  vec_ind[i] <- i
  vec_amount[i] <- length(dataHyp1$Goal_met[dataHyp1$Creator_nb_projects == i])
}

#create a table of vec_val and vec_ind as two columns with headers: index and percentage
tableHyp1 <- data.frame(vec_ind, vec_val, vec_amount)
tableHyp1

#make a barplot of the column vec_amount
barplot(tableHyp1$vec_amount, names.arg = tableHyp1$vec_ind, xlab = "Number of projects", ylab = "Number of projects of the creator", main = "Number of projects of the creator by number of projects of the creator")


#drop columns where nan exists
tableHyp1 <- tableHyp1[complete.cases(tableHyp1),]
tableHyp1


#make a barchart of tableHyp1
barplot(tableHyp1$vec_val, names.arg = tableHyp1$vec_ind, xlab = "Number of projects", ylab = "Percentage of projects that met their goal", main = "Percentage of projects that met their goal by number of projects of the creator")

#make a barchart of the number of projects per number of projects
barplot(tableHyp1$vec_amount, names.arg = tableHyp1$vec_ind, xlab = "Number of projects", ylab = "Number of projects of the creator", main = "Number of projects of the creator by number of projects of the creator")


barplot(dataHyp1$Creator_nb_projects,  names.arg = tableHyp1$vec_ind, xlab = "x", ylab = "y", main = "title")


```

## Results

### Hypothesis 1 results

```{r}

dataHyp1
dataHyp1$Creator_nb_projects
tableHyp1$vec_ind

```

Present the results of your analyses including descriptive statistics, regression tables, as well as any possible figures or visualizations that you made, e.g., those of the interaction effects.

## Discussion

What did we learn from what you found in your results, how do those findings relate to the ongoing debate in literature, and what can practitioners learn from that?

## Conclusion (?)

The description did not say a conclusion was needed, but I think it is a good idea to have one.

## References

the bib.tex file can go here. I have not yet added any references, but as we write they will be added.
